Simulating and detecting recovery in closed areas

### 2021-12-15 analysis/sim.Rmd
add notes

- include depth effect? (for now, no, just a spatial random field)
- what to do with time in conditioning model? s(year)? AR1? linear? independent? (for now s(year, k = 5))
- which tests to do after to assess recovery? (a bunch of GLMs etc. are here)
- what time spans to check? (starting with all historical HBLL N; 13 years; 7 survey years)
- what possible 'recoveries' to check? (starting with 5% per year)
- fix vs. simulate spatial and/or spatiotemporal random effects? (for now fixing spatial but not spatiotemporal fields)
- all MPAs together and/or look at some individual ones? (starting with all)
- which species to work with (starting with dogfish for no good reason other than lots of data)

@@

mesh <- make_mesh(m0$data, xy_cols = c("X", "Y"), cutoff = 15)
mesh$mesh$n
dat <- m0$data
m <- sdmTMB(response ~ 1 + s(year, k = 5), data = dat, family = tweedie(), mesh = mesh,
  silent = TRUE, time = "year", spatiotemporal = "IID")
m
```

@@

s <- sdmTMB::sdmTMB_simulate(
  formula = ~ 1 + restricted * year_covariate,
  data = dat,
  mesh = mesh,
  family = tweedie(),
  time = "year",
  # rho = 2 * plogis(m$model$par[['ar1_phi']]) - 1, # TODO!?
  rho = NULL,
  sigma_O = b$estimate[b$term == "sigma_O"],
  sigma_E = b$estimate[b$term == "sigma_E"],
  phi = b$estimate[b$term == "phi"],
  tweedie_p = b$estimate[b$term == "tweedie_p"],
  range = b$estimate[b$term == "range"],
  fixed_re = list(omega_s = omega_s, epsilon_st = NULL, zeta_s = NULL),
  # (Intercept), restrictedTRUE, year_covariate, restrictedTRUE:year_covariate
  B = c(b$estimate[b$term == "(Intercept)"], 0, 0, mpa_increase_per_year),
  seed = SEED
)
s <- rename(s, restricted = restrictedTRUE)
```

@@

```{r fit-sim-dat}
# s$year_covariate <- s$year_covariate - mean(s$year_covariate)
m2 <- sdmTMB(
  observed ~ 1 + restricted * year_covariate,
  data = s,
  mesh = mesh,
  time = "year",
  # spatiotemporal = "AR1",
  spatiotemporal = "IID",
  family = tweedie(),
  silent = TRUE
)

>>>>

- include depth effect? (for now, no, just a spatial random field) - yes?
- what to do with time in conditioning model? s(year)? AR1? linear? independent? (for now as.factor(year))) [factor?]
- which tests to do after to assess recovery? (a bunch of GLMs etc. are here) - at least fancy + GLM
- what time spans to check? (starting with all historical HBLL N; 13 years; 7 survey years) [2, 5, 10, 20]
- what possible 'recoveries' to check? (starting with 5% per year) [0, 0.02, 0.05, 0.1]
- fix vs. simulate spatial and/or spatiotemporal random effects? (for now fixing spatial but not spatiotemporal fields) [sim new?]
- all MPAs together and/or look at some individual ones? (starting with all) [do all; gwaii haanas; 1 or 2 others] --nearshore vs. offshore, number of samples...
- which species to work with (starting with dogfish for no good reason other than lots of data) - HBLL, count distribution,

- plotting out the closed areas... proportions closed
- plot cv stuff against MARE
- correlates of those metrics... proportion of abundance in MPAs
- turn fig 2 into supplement? or illustration... fit lm() and plot the slopes.
- plot against Fig 3 - precise temporally biased is bad
- plot both error things against CV (precision)

@@

mesh <- make_mesh(m0$data, xy_cols = c("X", "Y"), cutoff = 15)
mesh$mesh$n
dat <- m0$data
m <- sdmTMB(response ~ 0 + as.factor(year), data = dat, family = tweedie(), mesh = mesh,
  silent = TRUE, time = "year", spatiotemporal = "IID")
m
```

@@

s <- sdmTMB::sdmTMB_simulate(
  formula = ~ 1 + restricted * year_covariate,
  data = dat,
  mesh = mesh,
  family = tweedie(),
  time = "year",
  # rho = 2 * plogis(m$model$par[['ar1_phi']]) - 1, # TODO!?
  rho = NULL,
  sigma_O = b$estimate[b$term == "sigma_O"],
  sigma_E = b$estimate[b$term == "sigma_E"],
  phi = b$estimate[b$term == "phi"],
  tweedie_p = b$estimate[b$term == "tweedie_p"],
  range = b$estimate[b$term == "range"],
  fixed_re = list(omega_s = omega_s, epsilon_st = NULL, zeta_s = NULL),
  # (Intercept), restrictedTRUE, year_covariate, restrictedTRUE:year_covariate
  B = c(mean(b[grep("year", b$term),"estimate"]), 0, 0, mpa_increase_per_year),
  seed = SEED
)
s <- rename(s, restricted = restrictedTRUE)
```

@@

```{r fit-sim-dat}
# s$year_covariate <- s$year_covariate - mean(s$year_covariate)
m2 <- sdmTMB(
  observed ~ 1 + restricted * year_covariate,
  data = s,
  mesh = mesh,
  time = "year",
  spatiotemporal = "AR1",
  # spatiotemporal = "IID",
  family = tweedie(),
  silent = TRUE
)
